\chapter*{Preface}

This master thesis was conducted during the spring of 2024 at the \acrfull{ntnu}, Faculty of Information Technology and Electrical Engineering, Department of Computer Science. The thesis was written and accomplished in cooperation with NTNU SFI Centre for Geophysical Forecasting. \\

This marks the end of a long journey. Through ups and downs, I've made it to where I'm at today, writing these very words. I distinctly remember the day I entered university. I did not know what I'd like to focus on, given my various interests in computing from the age of 14. I stand here now, trying to bridge the gap between HPC and AI, with this thesis as my weapon in this fight. \\

I want to give my sincerest thanks to my supervisor, Ole Jakob Mengshoel, for listening to my monologues and providing guidance throughout this last year of my studies. I'd also like to thank my co-supervisor Anne Cathrine Elster, who was the main person guiding me towards this project. Furthermore, I'd like to thank the members of NTNU CGF. My deepest gratitude goes to Robin Rørstadbotnen for helping me get the necessary data and for always being available for questions, no matter what. Besides these people, I want to offer my gratitude to my friends and family for always sticking by my side, no matter what life throws at me. Without them, I'd be lost on the path of life. \\

Last of all, I want to thank my girlfriend, Ronja, the beacon of my heart, for staying by my side through good and bad days throughout this last year and for always supporting me through thick and thin.\\

Finally, as I leave my final lasting remarks before I ''hopefully'' graduate, I can only think of a few wise words regarding the future.
\quote{\textit{To infinity and beyond!} - Buzz Lightyear}

\begin{flushright}
Trondheim, Fall 2024  \\
\textit{Jørgen Aleksander Fagervik}
\end{flushright}